WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-06-10 method/sec_3-microservice.tex
Done scan reading

\cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}. Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interference.
Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as Interpolation, Transformation, and Validation, and we will also discuss in \cref{se:data_preprocess}. The Extension Adapter allows users to register new event-based or time-based triggers for the extensions. The extension scheduler triggers the events based on time and the extension handler triggers events based on data change.

>>>>

\cref{fi:wdias_micro_separation} shows the clear separation of microservices into the modules of the \acrshort{wdias}. Each adapter has a separate database, and the database is hosted separately for the high performance and to avoid interference.
Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running independently, such as interpolation, transformation, and validation, and we will also discuss in \cref{se:data_preprocess}. The Extension Adapter allows users to register new event-based or time-based triggers for the extensions. The extension scheduler triggers the events based on time and the extension handler triggers events based on data change.

### 2020-06-10 method/sec_4-db_struct.tex
Done scan reading

We used Redis \cite{RedisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support. It also supports Publisher Subscriber capabilities as an inbuilt feature. Redis is an open-source tool, and clustering is also available for scalability. Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension. Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data. The extension adapter uses Redis's Publisher Subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.

@@

\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}

@@

\begin{itemize}
  \item Supports query operations on geospatial data \cite{MongoDBMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}

>>>>

We used Redis \cite{RedisRedisDocumentation} as the in-memory database since it is a widely used database system with excellent support. It also supports Publisher Subscriber capabilities as an inbuilt feature. Redis is an open-source tool, and clustering is also available for scalability. Redis uses in-memory caching for fast access to the frequent access data in adapter-metadata and adapter-extension. Other than that, status adapter uses Redis as a key-value pair store to maintain the status for asynchronous requests handling while storing grid data. The extension adapter uses Redis's publisher subscriber capabilities to create a cronjob in extension scheduler service when a new extension creates with a trigger on time during data preprocessing.

@@

\begin{itemize}
  \item Open timeseries database with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}

@@

\begin{itemize}
  \item Supports query operations on geospatial data \cite{MongoDBMongoDBManual}
  \item Clustering and sharding available for scalability and reliability
\end{itemize}

### 2020-06-10 method/sec_5-data_preprocess.tex
Done scan reading

The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
Thus, we need to preprocess imported data before using them for weather forecasting. The WDIAS supports data preprocessing capabilities via extension modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation, but users can add more extensions as required.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/serial_interpolation.pdf}
    \caption{Serial interpolation.}
    \label{fi:serial_interpolation}
\end{figure}

\subsubsection{Spatial Interpolation}
During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/transformation.pdf}
    \caption{Time interval aggregration.}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}
Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/data_preprocess/validation.pdf}
    \caption{Timeseries data validation.}
    \label{fi:validation}
\end{figure}

>>>>

The data imported via import modules may have incorrect data, missing data, and incompatible data which cannot directly feed into simulation modules.
Thus, we need to preprocess imported data before using them for weather forecasting. The WDIAS supports data preprocessing capabilities via extension modules. The current system has a few inbuilt extensions such as interpolation, transformation, and validation, but users can add more extensions as required.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/serial_interpolation.pdf}
    \caption{Serial interpolation.}
    \label{fi:serial_interpolation}
\end{figure}

\subsubsection{Spatial Interpolation}
During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/transformation.pdf}
    \caption{Time interval aggregration.}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}
Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/validation.pdf}
    \caption{Timeseries data validation.}
    \label{fi:validation}
\end{figure}

### 2020-06-10 results/sec_1-test_plan.tex
Done scan reading

In \cref{se:high_level_design} we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination. We can map each of those modules to WDIAS modules, which provide the same functionalities as below.
\begin{enumerate}
    \item \emph{Import} modules - Integration modules
    \item \emph{Export} modules - Dissemination modules
    \item \emph{Extension} modules - Assimilation modules
\end{enumerate}

@@

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The Majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of NWMs. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}

>>>>

In \cref{se:high_level_design}, we discussed three modules of weather data integration and assimilation systems such as integration, assimilation, and dissemination. We can map each of those modules to WDIAS modules, which provide the same functionalities as below.
\begin{enumerate}
    \item \emph{Import} modules - Integration modules
    \item \emph{Export} modules - Dissemination modules
    \item \emph{Extension} modules - Assimilation modules
\end{enumerate}

@@

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of NWMs. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}
